Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-05-03 manu-draft.qmd
see gam scratch, these models tell a good story

>>>>

```{r}
# secchi on bottom is na issue
# also averaging all models by year in the bay segment for comparable sample size, fim/pdem limited to july - nov to minimize seasonal effect and when transect surveys completed for comparability
# < 17% for epc, much higher for fim/pdem so la not included, but can show la relatively stable in a plot
# epc is bonk becuase of disconnect between sites
# fim is good, makes sense, but otb is weird
# pdem temp makes sense for otb
```
